`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-19 inst/manuscript/manuscript.rmd
Add an abbreviaton section as requested by BMC Bioinformatics;
Minor fixes to mentionings of CRAN;

@@

# Availablility and Implementation {-}
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and Is available
"Comprehensive `R` Archive Network" (CRAN). It is thus install-- and loadable as
follows from within a functional `R` environment:

@@

The package is also uploaded to the comprehensive `R` archive network (CRAN) and
may thus be installed in its most up--to date version using 
`install.packages('flippant')` from within any appropriately configured `R`
installation.

>>>>

# Abbreviations {-}
ATP: 
  ~ Adenosine triphosphate

BSA:
  ~ Bovine serum albumin

CRAN:
  ~ The Comprehensive `R` Archive Network

MAD:
  ~ Median absolute deviation

NBD:
  ~ Nitrobenzoxadiazole

PPR:
  ~ Protein to phospholipid ratio

RAM:
  ~ Random--access memory

SSD:
  ~ Solid state disk

@@

# Availablility and Implementation {-}
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and is available
in The Comprehensive `R` Archive Network (CRAN). It is thus install-- and
loadable as follows from within a functional `R` environment:

@@

The package is also uploaded to The Comprehensive `R` Archive Network (CRAN) and
may thus be installed in its most up--to date version using 
`install.packages('flippant')` from within any appropriately configured `R`
installation.
